Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 paper.Rnw
changed name of variable based on change in data

# Create plot of the signatures
signatures %>%
  ggplot(aes(x = x/1000, y = sig)) + 
  geom_line() +
  facet_grid(land ~ .) +
  ylim(c(-4,6)) +
  theme_bw(base_family = ff, base_size = f9_fs) +
  theme(strip.background = element_blank()) +
  ylab("Surface Measurement (in microns)") +
  xlab("Relative Location (in millimeters)")

>>>>

# Create plot of the signatures
signatures %>%
  ggplot(aes(x = x/1000, y = y)) + 
  geom_line() +
  facet_grid(land ~ .) +
  ylim(c(-4,6)) +
  theme_bw(base_family = ff, base_size = f9_fs) +
  theme(strip.background = element_blank()) +
  ylab("Surface Measurement (in microns)") +
  xlab("Relative Location (in millimeters)")
